Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-05 src/paper.tex
update

We use the output from hidden layers 1, 3, 7, 12, 18, 23 from WavLM Large for tokenization. 
We use embedding dimension 1024,  4 transformer 
encoders each with 16 heads and MLP with hidden dimension of 1024 in the cross attention module. We 
use layer norm after the cross attention module. 
We use separate embedding tables in attention embedding module for reference and mixed speech due to our observations that not 
sharing embeddings does slightly better than sharing embeddings. The small version of TSELM-S uses 
embedding dimension \(d\) = 256, absolute sinusoidal positional embedding, and there are

>>>>

We use the output from hidden layers 1, 3, 7, 12, 18, 23 from WavLM Large for tokenization. 
We use embedding dimension 1024,  4 transformer 
encoders each with 16 heads and MLP with hidden dimension of 1024 in the cross attention module. We 
use layer norm after the cross attention module. 
We use separate embedding tables in attention embedding module for reference and mixed speech due to our observations that not 
sharing embeddings does slightly better than sharing embeddings. The LM of small version TSELM-S uses 
embedding dimension \(d\) = 256, absolute sinusoidal positional embedding, conformer encoders as backbone of LM. The conformer encoder is composed of 
6 layers with kernel size 31 each with 4 heads and an MLP with hidden dimension 2048. The medium version TSELM-M uses \(d\) = 512 with 8 layers and 8 heads and the large version TSELM-L uses 
\(d\) = 768 with 12 layers and 16 heads.
